Frequency of dwarf and massive galaxy pairs in the IllustrisTNG cosmological simulation

### 2023-02-11 paper/pears.tex
pulling to get new vel dist 1000 plot

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation_distribution.png}
  \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines. 
  At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively). However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
  % \kc{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
   \todo{change color of med lines, add z=4, replace with 1000 reals }
    }
  \label{fig:sep-dist}
\end{figure*}

@@

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{velocity_distribution.png}
  \caption{
  Normalized distribution of relative velocities between primary and secondary halos for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines. 
  %
  The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts. The distribution of velocities for major and minor pairs is roughly equivalent. 
  \todo{finish caption, change color of med lines, add z=4, replace with 1000 reals}
    }
  \label{fig:vel-dist}
\end{figure*}
%%%

>>>>

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation_distribution_1000.png}
  \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines. 
  At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively). However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
    }
  \label{fig:sep-dist}
\end{figure*}

@@

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{velocity_distribution_1000.png}
  \caption{
  Normalized distribution of relative velocities between primary and secondary halos for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median relative velocity of each pair type from Fig.~\ref{fig:vel} is shown in solid (major) and dotted (minor) vertical black lines. 
  %
  The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts. 
  At $z=0$, typical dwarf pair relative velocities are $0-200\,\kms$, while at $z=4$ they are $0-300\,\kms$. 
  Massive pairs typically have relative velocities between $0-300\,\kms$ at z=0 and $0-400\,\kms$ at $z=4$.
  The distribution of velocities for major and minor pairs is roughly equivalent within each mass range. 
    }
  \label{fig:vel-dist}
\end{figure*}
%%%
